CS246: Twitter Purification

### 2014-06-08 Paper.tex
Adding ShiWen's related work

\section*{Related work}
\paragraph{} Aspell's algorithm uses a combination of DoubleMetaphone and weighted edit distance to find correction candidates.\footnote{\href{http://aspell.net/0.50-doc/man-html/8_How.html}{8. How Aspell Works}} Search engines such as Google use a more similar method to what was outlined here, using a combination of probabilistic data and edit distance.

>>>>

\section*{Related work}
\paragraph{} Aspell's algorithm uses a combination of DoubleMetaphone and weighted edit distance to find correction candidates.\footnote{\href{http://aspell.net/0.50-doc/man-html/8_How.html}{8. How Aspell Works}} Search engines such as Google use a more similar method to what was outlined here, using a combination of probabilistic data and edit distance.
Subhabrata Mukherjee, etc published a paper that dealt with sentiment analysis of tweets. In their pre-processing work, they used a Twitter specific spellchecking algorithm, which utilized vowel exchange, dropping of vowels, text compression, squeeze, and edit distance methods. They had intended to also deal with phonetic transformation, segmentation with punctuation, segmentation with compound words, etc.
